Abstractions for Multi-Sorted Substitutions

### 2023-08-08 paper/paper.tex
Update.

  A renaming \texttt{S₁ →ᵣ S₂} maps variables from \texttt{S₁} to
  variables from \texttt{S₂}.
  A substitution \texttt{S₁ →ₛ S₂} maps variables from \texttt{S₁} to
  terms containing variables from \texttt{S₂}.

@@

  \subsection{Unifying Renamings \& Substitutions}
  A well-known problem with DeBruijn-indices is that full substitution
  cannot be defined directly by structural recursion on the term.
  The usual workaround is to define renamings first and use them
  to weaken the terms in substitutions when going under binders.

  While this keeps lemmas simple (requiring only structural induction),
  it duplicates the amount of work as all operations and lemmas have
  to be defined and proved for both renamings and substitutions.

>>>>

  A renaming \texttt{S₁ →ᵣ S₂} maps variables from \texttt{S₁} to
  variables from \texttt{S₂}.
  A substitution \texttt{S₁ →ₛ S₂} maps variables from \texttt{S₁} to
  terms with free variables from \texttt{S₂}.

@@

  The usual workaround is to define renamings first and use them
  to weaken the terms in substitutions when going under binders.
  While this keeps lemmas simple (requiring only structural induction),
  it duplicates the amount of work as all operations and lemmas have
  to be defined and proved for both renamings and substitutions.
